method

### 2022-02-17 06_Paper/ER-ED/method.Rmd
import marker file

datalist_EMG = lapply(list.files(here("04_RawData", "pilot", "ER-ED/EMG/analysis"), pattern = '*_Peaks.txt', full.names = TRUE),
                          read.table, stringsAsFactors = FALSE, header = TRUE)

@@

  tmp = data.frame(datalist_EMG[[i]][["Filename"]], 
                   datalist_EMG[[i]][["Segment"]], 
                   datalist_EMG[[i]][["T0T6000Corr.ASNM"]], 
                   datalist_EMG[[i]][["T0T6000Lev.ASNM"]])
  colnames(tmp) = names(data_EMG)

>>>>

datalist_EMG <- lapply(list.files(here("04_RawData", "pilot", "ER-ED", "EMG", "analysis"), pattern = '*_Peaks.txt', full.names = TRUE),
                          read.table, stringsAsFactors = FALSE, header = TRUE)
datalist_EMG_Marker <- lapply(list.files(here("04_RawData", "pilot", "ER-ED", "EMG", "analysis"), pattern = "*.Markers", full.names = TRUE),
                              read.table, stringsAsFactors = FALSE, header = TRUE, skip = 1, row.names = NULL)

@@

  tmp = data.frame(datalist_EMG[[i]][["Filename"]], 
                   datalist_EMG_Marker[[i]][["Description"]], 
                   datalist_EMG[[i]][["T0T6000Corr.ASNM"]], 
                   datalist_EMG[[i]][["T0T6000Lev.ASNM"]])
  colnames(tmp) = names(data_EMG)
